Verifying Demonstrations

### 2019-05-28 paper/DB-anon-cred.tex
Rewrites DB-Schnorr alg description to use UWBPR

We also deviate from the normal technique of one-bit challenges and responses 
otherwise used in \ac{DB} protocols.
\Textcite{UWBwithPulseReordering} proposed a secure encoding for the physical 
layer which removes the requirement of only using single-bit challenges and 
responses for distance bounding.
However, their protocol only works for relay attacks and cannot handle distance 
fraud.
This is due to a requirement of the protocol that the prover and verifier must 
share a secret, and thus must be mutually trusted.

@@

We present the protocol in \cref{SchnorrFigure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

@@

    % null
    & \(\ProtoSendLeft{c_0, c_1}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
    \\

    \(s_0\gets \rho - c_0\alpha \pmod q\)
    &
    & \(b\rgets \bin\)
    \\

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    &
    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
        l, j\gets 0\)} \\

@@

    % null
    & \(\ProtoSendLeft{b_i}\)
    & \(b_i\gets B[i]\)
    \\

    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

    \(j \gets j + b_i\)
    &
    &
    \\

@@

    % null
    &
    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
      Accept if \(R = g^{s_b} A^{c_b}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
The verifier will request all \(|q|\) response-bits from one challenge (say 
\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
Then the verifier can authenticate the prover by checking if \(R = 
  g^{s_b}A^{c_b}\).

>>>>

We also deviate from the normal technique of one-bit challenges and responses 
otherwise used in \ac{DB} protocols.
\Textcite{UWBPR} proposed a secure encoding for the physical 
layer which removes the requirement of only using single-bit challenges and 
responses for distance bounding.
However, their protocol only works for relay attacks and cannot handle distance 
fraud.
This is due to a requirement of the protocol that the prover and verifier must 
share a secret, and thus must be mutually trusted.

@@

Thanks to \textcite{UWBPR} we can keep the Schnorr protocol 
almost as is, relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical 
layer.
The only concern, for now, is \acl{DBTF}.
(We deal with \acl{DBDF} later.)

We present the protocol in \cref{SchnorrFigure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
Further, let
\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
key~\(k\) and finally
\(\Delta t\gets \UWBPRtime\) denote the time between sending and receiving.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[k, g, q, A]\):
    \\
    \midrule

@@

    Load \(k\) into \(\UWBPR\)
    &
    & Load \(k\) into \(\UWBPR\)
    \\

@@

    \(s_0\gets \rho - c_0\alpha \pmod q\)
    & \(\ProtoSendLeft{c_0, c_1}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
    \\

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    &
    &
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\

    \text{Ready}
    & \ProtoSendRight{\text{Ready}}
    & \\

@@

    % null
    & \(\ProtoSendLeft{b}\)
    & \(b\rgets \bin\)
    \\

    Fetch \(s_b\)
    & \(\ProtoSendRight{s_b}\)
    & Record \(\Delta t\)
    \\

@@

    % null
    &
    & Accept if \(R = g^{s_b} A^{c_b}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated in full to achieve the desired soundness 
    and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

During one round, in the setup phase, the prover commits to a random nonce: 
more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
\(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

In the \ac{DB} phase, the prover notifies the verifier that he has computed 
\(s_0, s_1\).
The verifier chooses one bit, \(b\), uniformly randomly and sends it as a 
challenge to the prover and starts measuring the time of flight.
The prover replies with \(s_b\).
The verifier stops the measurement and verifies that \(R = g^{s_b}A^{c_b}\).
